Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
tried to add the analysis of RDFS

\subsection{Parallelly Tractable Materialization of DHL}

@@

\subsection{Parallelly Tractable Materialization of DHL($\circ$)}

@@

>>>>

\subsection{Parallelly Tractable Materialization of DHL}
\label{sec:DHL}

@@

\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
\label{sec:DHLo}

@@

\subsection{The Parallel Tractability of the Reasoning on RDFS Ontologies}

In this part, we discuss about the parallel tractability of the reasoning on RDFS ontologies.
Although RDFS is not a standard description logic, it can be described by a subset of the DL axioms \cite{GrosofHVD03}.
The correspondence between the RDFS statements and the DL axioms is listed in Table~\ref{tab:rdfs}.
We call the RDFS statements in the form of (1-4) \emph{the schema data}
(which correspond to TBox axioms), the statements in the form of (5) and (6)
\emph{the instance data} (which correspond to ABox axioms).

\begin{table}
\begin{center}
\begin{tabular}{lcc}
\multicolumn{3}{c}{\textbf{Table~\ref{tab:rdfs}: The RDFS statements and the corresponding DL axioms}}\\
\hline
&~~~~~~~~~~~~~RDFS statements~~~~~~~~~~~~~&~~~~~~~~~~~~~~Axiom~~~~~~~~~~~~~~\\
\hline
\hline
(1)&$P~~\texttt{rdfs:domain}~~C$& $\top\sqsubseteq\forall P^-.C$\\

(2)&$P~~\texttt{rdfs:range}~~C$& $\top\sqsubseteq\forall P.C$\\

(3)&$B~~\texttt{rdfs:subClassOf}~~C$& $B\sqsubseteq C$\\

(4)&$R~~\texttt{rdfs:subPropertyOf}~~S$& $R\sqsubseteq S$\\
\hline
(5)&$a~~\texttt{rdf:type}~~C$& $C(a)$\\

(6)&$a~~R~~b$& $R(a,b)$\\
\hline
\end{tabular}
\label{tab:rdfs}
\end{center}
\end{table}

The original rule set for the reasoning task of RDFS ontologies is
given in \cite{RDFSrec04}. By applying the rules in this rule set,
new schema data would be derived. Thus, the reasoning task of RDFS
is different from the task of materialization. Further, an RDFS ontology allows
statements about blank nodes which play as variables. This semantically
leads to infinite entailments. The author of \cite{Horst05} proves that
the original rule set is incomplete with the restriction that
blank nodes cannot occur in predicate positions. By loosening this restriction,
the rule set turns out to be complete. The computational complexity
of the reasoning task on RDFS ontologies is shown to be NC-complete \cite{Horst05},
which is not considered to be prallel-tractable.

The situation of path twisting may also happen when conducting reasoning
on RDFS ontologies. Suppose $R_{subp}$ denotes the RDFS built-in property $\texttt{rdfs:subPropertyOf}$.
We define the other three properties $R_1$, $R_2$ and $R_3$ by the following axioms:
$R_1\sqsubseteq R_{subp}, R_2\sqsubseteq R_{subp}$ and $R_{subp}\sqsubseteq R_3$.
It can be checked that these three axioms entail the complex RIA $R_1\circ R_2\sqsubseteq R_3$ (denoted by $\beta$).
If axiom $\beta$ does not meet the simple-role restriction (see Section~\ref{sec:DHLo}),
the situation of path twisting may also happen as shown in Example~\ref{exp:complexRIA}.

In this work, we study the task of materialization. Similarly, we can only focus on
the entailments of new instance data for the target RDFS ontologies. To this end,
we assume that any class of RDFS ontologies has the same schema data (\uppercase\expandafter{\romannumeral1}). In this way,
the axioms like $\beta$ cannot contribute to the computational complexity, since they
only apply to schema data. Further, we restrict that blank nodes cannot occur in
any class of RDFS ontologies (\uppercase\expandafter{\romannumeral2}). This allows an RDFS ontology
being expressed in DHL (see Table~\ref{tab:rdfs}). Based on the two restrictions (\uppercase\expandafter{\romannumeral1})
and (\uppercase\expandafter{\romannumeral2}), the reasoning task on RDFS ontologies
is parallel-tractable (see Section~\ref{sec:DHL}).
